\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-26 doc/paper.tex
Fixes #61.

	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing
	the minutiae of tool's development, we will give a basic example of how
	to use the tool. For this, we will answer this question: \textit{ What kinds of
		functions do people use to define the condition in an IF function?} \par

>>>>

	\subsection{Walkthrough of the Tool} \label{sec:walkthrough}Before discussing
	the minutiae of tool's development, we will give a basic example of how
	to use the tool. For this, we will work from the visualization built on the Enron
	corpus to answer this question: \textit{ What kinds of
		functions do people use to define the condition in an IF function?} \par
